HO unification from object language to meta language

### 2024-03-21 paper/appendix.tex
small cleanup in comp

  type comp fo.fm -> ho.tm -> mappings -> mappings -> links -> 
    links -> ho.subst -> ho.subst -> o.
  comp (fo.fcon X) (ho.con X)        Map1 Map1 L1 L1 S1 S1.
  comp (fo.flam F) (ho.uva E0 Scope) Map1 Map2 L1 L3 S1 S3 :-
    (pi x\ maybe-eta x (F x) [x]), !,
    mem.new S1 E0 S2,
    comp-lam F F1 Map1 Map2 L1 L2 S2 S3,
    (pi x\ locale x => get-scope (F1 x) Scope), 
    NewLink = ho.val(link-eta (ho.uva E0 Scope) (ho.lam F1)), 
    L3 = [NewLink| L2].
  comp (fo.flam F) (ho.lam F1)       Map1 Map2 L1 L2 S1 S2 :- 
    comp-lam F F1 Map1 Map2 L1 L2 S1 S2.
  comp (fo.fuva N) (ho.uva M []) Map1 Map2 L L S S1 :- 
    alloc Map1 Map2 (fv N) (hv M (arity z)) S S1.
  comp (fo.fapp [fo.fuva N|Ag]) (ho.uva M' Scope) Map1 Map3 L1 L3 S1 S4 :- !,
    split-pf Ag PF NPF,
    forall2 (x\y\ comp x y _ _ _ _ _ _) PF PF1,
    fold6 comp NPF NPF1 Map1 Map2 L1 L2 S1 S2,
    len PF Arity, 
    alloc Map2 Map3 (fv N) (hv M (arity Arity)) S2 S3,
    if (NPF = []) 
      (Scope = PF1, M' = M, S3 = S4, L2 = L3)
      (get-scope (ho.app {std.append PF1 NPF1}) Scope, 
        mem.new S3 M' S4,
        L3 = [@val-link-beta (ho.uva M' Scope) (ho.app[ho.uva M PF1 | NPF1]) | L2]).
  comp (fo.fapp A) (ho.app A1) Map1 Map2 L1 L2 S1 S2 :- 
    fold6 comp A A1 Map1 Map2 L1 L2 S1 S2.

@@

  progress-beta-link (ho.uva _ _ as T) (ho.app[ho.uva Ad1 Scope1 | L1] as T1) S1 S3 NewLinks :-
    std.append Scope1 L1 Scope1L,
    split-pf Scope1L Scope2 L2,
    not (Scope1 = Scope2), !,
    mem.new S1 Ad2 S2,
    len Scope1 Scope1Len,
    len Scope2 Scope2Len,
    make-eta-link Scope1Len Scope2Len Ad1 Ad2 [] LinkEta S2 S3,
    if (L2 = []) (NewLinks = LinkEta, T2 = ho.uva Ad2 Scope2) 
      (T2 = ho.app [ho.uva Ad2 Scope2 | L2], 
      NewLinks = [@val-link-beta T T2 | LinkEta]).

>>>>

  type comp fo.fm -> ho.tm -> mappings -> mappings -> links -> 
    links -> ho.subst -> ho.subst -> o.
  comp (fo.fcon X) (ho.con X)        Map1 Map1 L1 L1 S1 S1.
  comp (fo.flam F) (ho.uva E0 Scope) Map1 Map2 L1 L3 S1 S3 :-
    (pi x\ maybe-eta x (F x) [x]), !,
      mem.new S1 E0 S2,
      comp-lam F F1 Map1 Map2 L1 L2 S2 S3,
      (pi x\ locale x => get-scope (F1 x) Scope), 
      NewLink = ho.val(link-eta (ho.uva E0 Scope) (ho.lam F1)), 
      L3 = [NewLink| L2].
  comp (fo.flam F) (ho.lam F1)       Map1 Map2 L1 L2 S1 S2 :- 
    comp-lam F F1 Map1 Map2 L1 L2 S1 S2.
  comp (fo.fuva N) (ho.uva M []) Map1 Map2 L L S S1 :- 
    alloc Map1 Map2 (fv N) (hv M (arity z)) S S1.
  comp (fo.fapp [fo.fuva N|Ag]) (ho.uva M Scope) Map1 Map2 L1 L1 S1 S2 :-
    pattern-fragment Ag, !,
      fold6 comp Ag Scope Map1 Map1 L1 L1 S1 S1,
      len Ag Arity, 
      alloc Map1 Map2 (fv N) (hv M (arity Arity)) S1 S2.
  comp (fo.fapp [fo.fuva N|Ag]) (ho.uva M' Scope) Map1 Map3 L1 L3 S1 S4 :- !,
    pattern-fragment-prefix Ag PF NPF,
      fold6 comp PF PF1 Map1 Map1 L1 L1 S1 S1,
      fold6 comp NPF NPF1 Map1 Map2 L1 L2 S1 S2,
      len PF Arity, 
      alloc Map2 Map3 (fv N) (hv M (arity Arity)) S2 S3,
      get-scope (ho.app {std.append PF1 NPF1}) Scope, 
      mem.new S3 M' S4,
      L3 = [@val-link-beta (ho.uva M' Scope) (ho.app[ho.uva M PF1 | NPF1]) | L2].
  comp (fo.fapp A) (ho.app A1) Map1 Map2 L1 L2 S1 S2 :- 
    fold6 comp A A1 Map1 Map2 L1 L2 S1 S2.

@@

  progress-beta-link (ho.uva _ _ as T) (ho.app[ho.uva Ad1 Scope1 | L1] as T1) S1 S3 NewLinks :-
    std.append Scope1 L1 Scope1L,
    pattern-fragment-prefix Scope1L Scope2 L2,
    not (Scope1 = Scope2), !,
    mem.new S1 Ad2 S2,
    len Scope1 Scope1Len,
    len Scope2 Scope2Len,
    make-eta-link Scope1Len Scope2Len Ad1 Ad2 [] LinkEta S2 S3,
    if (L2 = []) (NewLinks = LinkEta, T2 = ho.uva Ad2 Scope2) 
      (T2 = ho.app [ho.uva Ad2 Scope2 | L2], 
      NewLinks = [@val-link-beta T T2 | LinkEta]).
